The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-10-30 sections/discuss.tex
Resection the discussion and add new figures

@@

\subsection{Sensitivity to climate forcing}

\subsection{Potential method improvements}

>>>>

\subsection{Comparison of forcing climatologies}
\emph{Fig. topo-prec: there are large differences in climate forcing. (1) Temperature diff are due to topography, except for cold NCAR. (2) Precipitation diff related to orographic effects, except for CFSR (Fig.~\ref{fig:tempheatmap}-\ref{fig:oroprecip}).}

\subsection{Sensitivity to climate forcing}
\emph{Most differences are due to precip, except for NCAR (Fig.~\ref{fig:biatm}).}

@@

\subsection{Sensitivity to glaciation duration}
\emph{Glaciation duration has upper bound, but it may have been shorter. Shorter gives better results, so 10Ka may be too much, or at least it shows that our approach may be too simplistic. Longer gives worst result: the LGM CIS is not at steady-state (Fig.~\ref{fig:durationstack}).}

\subsection{Other potential method improvements}
